---
title: "Red wine quality"
output:
  html_document:
    df_print: paged
---
In this work we are going to predict the __Red_wine quality__ based on a number of chemical properties like pH, alcohol...etc



###*__Introduction:__* 

The predidctors are __10__ tests made on the wine (e.g __PH__ value) and the output is made by __3__ experts, where each one rates the quality of the wine from __0__ (_very bad_) to __10__ (_very exellent_).
The dataset contains __1,599__ measurments and __11__ variables.

####*__1- Loading data and required packages: __*

Loading the needed packages for data manupilation, visualization and model building...
```{r message=FALSE ,echo=FALSE}
library(data.table)
library(dplyr)
library(tidyr)
library(lubridate)
library(rpart)
library(ggplot2)
library(caret) 
library(AppliedPredictiveModeling)
```
Loading the *csv* file containing the dataset...
```{r}
setwd("C:/Users/folio/Desktop/Red_wine_quality_analysis-master/data")
data <- read.csv("winequality-red.csv", header = TRUE,sep = ";")
```

####*__2- A quick view on the dataset: __*
```{r}
str(data)
```

A general summary of the dataset ( *min*, *mean*, *max*, *1st Q*, *3d Q* and the *median* of each variable)...
```{r}
summary(data)
```

####*__3- Rpart model: __*

In this section each variable, starting from the *quality*, will be explored to make some observations from:

* __*Spectral analysis *__: *distribution*, *skewness* and *kurtosis* using __Histogram__ plots.

* __*Central tendecy and Dispersion measurements*__: *Mean*, *Median*, *Min*, *Max*, *Mode*, *Range*, *IQR*, *variance*, *SD*, *Outlines* with the help of __Boxplots__. 

* __*The existance of missed values*__.

##### *__ quality: __*

a quick summary...
```{r}
summary(data$quality)
```

Boxplot to visualize the centrality of *quality*
```{r}
ggplot(data = data, aes(1,y=quality))+
  geom_boxplot(fill = "white", colour = "#3366FF",outlier.color = "blue")+
  geom_jitter(width = 0.2,color = "red",alpha= 0.2)


```
Histogram...
```{r}
ggplot(data=data ,aes(quality))+
 geom_histogram(position  = "identity" ,binwidth = 0.5,color = "#3366FF",aes(mapping=0.1))+
  
  geom_density(color = "blue")

```
Histogram of all variables
```{r}
td <- gather(data, key = "key", value = "value")
ggplot(td, aes(x = value)) +
 geom_histogram(fill = "grey20", binwidth = .01) +
  facet_wrap(~key , scales = "free")
```
All variables against quality
```{r}
td2 <- gather(data,-quality,-pH, key = "key", value = "value")
ggplot(td2, aes(x = quality,y = value)) +
  geom_point(alpha =0.4) +
  geom_smooth(method = "lm")+
  facet_wrap(~key , scales = "free")
```




```{r}
tree <- rpart(quality ~ ., 
  data = data)
plotcp(tree)
plot(tree, uniform = TRUE)
text(tree, use.n = TRUE, cex = 0.75)
```

